### 2022-05-08 manuscript.Rmd
Fix harmonic mean / SE for gender differences

    # Compute standard error of Cohen's d, using harmonic mean of sample sizes
    ni = female_n + male_n,
    nhi = (female_n * male_n) / ni,
    vi = (df * 2 * (1 + (gi^2 * nhi * 0.5))) / ((df - 2) * nhi) - (gi^2 / j^2),
    sei = sqrt(vi)
  ) %>%
  # Remove experiments that didn't provide an effect size
  filter(!is.na(gi)) -> dat_gender

@@

Where $\tilde{n}$ is the harmonic mean of the group sizes
(i.e., $\tilde{n}=\frac{n_\text{female}n_\text{male}}{n_\text{female}+n_\text{male}}$)
and ${df}$ are the degrees of freedom as provided in row (1) of Table 2.
A sensitivity analysis highlights the stability of the effect size computed using the Bayesian meta analysis (Supplementary Table 5).

>>>>

    # Compute standard error of Cohen's d, using harmonic mean of sample sizes
    ni = female_n + male_n,
    nhi = 2 / (1 / female_n + 1 / male_n),
    vi = (df / (df - 2)) * (2 / nhi) * (1 + gi^2 * (nhi / 2)) - (gi^2 / (j^2)),
    sei = sqrt(vi)
  ) %>%
  # Remove experiments that didn't provide an effect size
  filter(!is.na(gi)) -> dat_gender

@@

Where $\tilde{n}$ is the harmonic mean of the group sizes
(i.e., $\tilde{n}=\frac{2}{n_\text{female}^{-1}+n_\text{male}^{-1}}$)
and ${df}$ are the degrees of freedom as provided in row (1) of Table 2.
A sensitivity analysis highlights the stability of the effect size computed using the Bayesian meta analysis (Supplementary Table 5).
